Two genera pathway association

### 2020-02-05 scripts/32_two_genera.Rmd
update

@@

bac_genera <- read_csv('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/data/Bacteroidetes_genus.csv') %>% 
  pull(genus)

@@

>>>>

genus_entero %>% 
  write_tsv('../data/two_genera/genus_entero_pw_df.tsv')

@@

bac_genera <- read_csv('../data/two_genera/Bacteroidetes_genus.csv') %>% 
  pull(genus)

@@

sig_CR %>% 
  head() %>% 
  kable() %>% 
  kable_styling(full_width = F)
```
```{r}

pheatmap(
  bact_matrix[,colnames(bact_matrix) != "2098A"],
  #color=bwrPalette, 
  annotation_col = annot,
  show_rownames = T,
  show_colnames = TRUE,
  filename = '../figs/heatmap/bact_heatmap.jpg',
  height = 18,
  width = 28,
  cluster_rows = T,
  cluster_cols = T
)
```

```{r}
# because of the sparsity that we turn the count into 0 and 1

entero_matrix[entero_matrix > 0] = 1

bact_matrix[bact_matrix > 0] = 1

pheatmap(
  bact_matrix,
  #color=bwrPalette, 
  annotation_col = annot,
  show_rownames = F,
  show_colnames = TRUE,
  filename = '../figs/heatmap/bact_heatmap_binary.jpg',
  height = 18,
  width = 20,
  cluster_rows = T,
  cluster_cols = T
)

pheatmap(
  entero_matrix,
  #color=bwrPalette, 
  annotation_col = annot,
  show_rownames = F,
  show_colnames = TRUE,
  filename = '../figs/heatmap/entero_heatmap_binary.jpg',
  height = 18,
  width = 20,
  cluster_rows = T,
  cluster_cols = T,
  main = 'entero genus'
)
```
